A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-04-12 doc/paper.tex
R1C1 - fixing :/! in quotes bug.

\section{Case Study}

>>>>

\section{Case Study}
The obvious question to pose to any visualization is this: Why does it matter that we see this way? In other words, it is not enough to prove that something can be visualized; instead we must also demonstrate what we can be gained from any particular visualization. As such, we raised a few tasks in the introduction in which we thought the tool could help: identifying places for API improvement, detecting bad smells or common programmer misunderstanding, and guiding spreadsheet education. Thus, to demonstrate the tool's applicability, we sought out places in the tree which best exemplify these respective concerns.

\subsection{Bad Smells}
Fowler's (?) seminal description of code smells underscored
an important point of code quality: between perfect code and 
bug-crippled spaghetti,  there is a spectrum of code designs 
which, by themselves, are not faulty but nevertheless may
point to problems and vulnerabilities in how code is written.
Code smells, as we call them, soon commanded attention and earned wide-ranging 
applicability, eventually making it to the art of spreadsheet design.
Since then, Hermans and others catalog the odors of spreadsheets, 
often built off Fowler's (?) original specifications to articulate
the subtle problems in spreadsheet design. \par 
Collected, some of the intra-spreadsheet smells fall well within the
purview of this visualization tool. Some such smells can be found
in a figure [FIGURE]. \par 
The smells described above, then, entail a corresponding structure
visible in the visualization: the deeper a branch runs, or the
taller the range of arguments, the more it emits the stench of suboptimal
design. \par 
To be sure, these rank occurrences must be leveraged with their prevalence
across the dataset. One person's anomaly, though perhaps still interesting,
will not be as impactful as a smell of thousands. \par
Some examples are meaningful not for the space they take up but for how
they clash with the expectations around a function. For example, Excel
offers a number of functions that accept any number arguments given to 
them, up to a resource-defined limit. SUM and CONCATENATE are two such functions:
adding more arguments simply adds or appends that element in the same way
as every previous argument. Strange cases were found, then, in the cases where
these functions were used with only one argument. \par
Hermans, in her paper on the nuances of VLOOKUP and its common misuses, explore
the problem of the final, optional argument. A tool there helped, but how might
a visualization such as this illuminated the same?

\subsection{Education}
Learning by example has long been a cornerstone of effective teacher techniques:
by showing the student a concrete example of something, rather than dwelling in
the realm of abstract description, comprehension increases [I'm sure there's a cite
out there somewhere.] This is no different in software, where every explanation of
a tricky programming concept is much untangled by the illustrative stub. Even APIs,
researchers have found, by the inclusion of an in-practice example of the function
described. Spreadsheet programming, then, should not be essentially different: 
examples of spreadsheet functions in use

\section{Limitations}
